Locality and Computational Reliability of Linear Response Calculations for Molecular Systems

### 2018-10-18 AnalyticStructure_main.tex
update

% Useful packages
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{mathtools,braket}
\usepackage{tikz}
\usepackage{xifthen}
%\pgfplotsset{compat=1.15}

@@

\section{Introduction}
Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the 
computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
For example, it may be in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
other quantities that might be then used to \emph{predict} or \emph{interpret} experiments.
Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
that a given computational model provides for a specific set of quantities, regardless of their potential agreement with 
experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertainties
of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
employing the same model can be compared.

@@

The analysis described above has shown that the building blocks of the response density $\{\ket{f_p(\omega)}\}$ 
are susceptible to exhibit bound-state long-range behavior \emph{only} when $\omega < |\eps_p|$, 
while they behave as unbound states for values of $\omega$ above the threshold levels.
This fact has interesting implications in the evaluation of LR quantities. Indeed, writing the response 
density in terms of FS implies that 
\be\lb{LinearResponseFunctDef2}
\braket{\delta\op O}_\Phi(\omega) = 2\mathrm{Re} \left(\sum_p \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \;.
\ee
Let us suppose that also the observable of interest $\op O$ exhibits the locality properties introduced for the potentials $ \op V$, $\op \Phi$ and $\op V'$.
Once again, it would be enough to consider a local operator for this condition to be met.

@@

As an example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in 
three distinct real-space computational setups, which differs for the dimension of 
the computational domain. 
Results reported in figure \ref{co_spectrum} evidences a typical behavior: the curves are almost coincident in the below threshold regime,
whereas the effect of the computational setup are clearly visible for values of $\omega$ that exceed the threshold value.
For these high-frequency regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008},
which are -- as already noticed -- more than sufficient below threshold.

>>>>

% Useful packages
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{mathtools,braket}
\usepackage{tikz}
\usepackage{xifthen}
%\pgfplotsset{compat=1.15}
\usepackage[markup=underlined]{changes}
\definechangesauthor{dal}
\definechangesauthor{gen}

@@

\section{Introduction}
\added[id=dal]{Testo nuovo}.
\deleted[id=dal]{lallero}

Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the 
computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
For example, it may be in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
other quantities that might be then used to \emph{predict} or \emph{interpret} experiments.
Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
that a given computational model provides for a specific set of quantities, regardless of their potential agreement with 
experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertainties
of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
employing the same model can be compared.

@@

The analysis described above has shown that the building blocks of the response density $\{\ket{f_p(\omega)}\}$ 
are susceptible to exhibit bound-state long-range behavior \emph{only} when $\omega < |\eps_p|$, 
while they behave as unbound states for values of $\omega$ above the threshold levels.
This fact has interesting implications in the evaluation of LR quantities. Indeed, writing the response 
density in terms of FS implies that \added[id=dal]{(equation for the response density modified)}
% \be\lb{LinearResponseFunctDef2}
% \braket{\delta\op O}_\Phi(\omega) = 2 \mathrm{Re} \left(\sum_p \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \;.
% \ee
\be\lb{LinearResponseFunctDef2}
\braket{\delta\op O} = \sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \;.
\ee
Let us suppose that also the observable of interest $\op O$ exhibits the locality properties introduced for the potentials $ \op V$, $\op \Phi$ and $\op V'$.
Once again, it would be enough to consider a local operator for this condition to be met.

@@

As an example in support of these arguments we compare the \replaced[id=dal]{dynamical polarizability $\alpha(\omega)$}{absorption spectrum} of a $CO$ molecule computed in three distinct real-space computational setups, which differs for the dimension of the computational domain. 
Results reported in \replaced[id=dal]{the two panels of figure \ref{co_spectrum} show the real and imaginary part of $\alpha(\omega)$, respectively. In all the cases a typical behavior emerges}{evidences a typical behavior}: the curves are almost coincident in the below threshold regime,
whereas the effect of the computational setup are clearly visible for values of $\omega$ that exceed the threshold value.
For these high-frequency regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008},
which are -- as already noticed -- more than sufficient below threshold.
